Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-18 analysis/normalized.Rmd
Correct the percentage of non-default environments.

Minimized:
```{r}
widespread_minimized <- E_cano %>%
  group_by(minimized) %>%
  summarize(n_call_sites = n_distinct(src_ref), proportion = ratio(n_call_sites, nb_call_sites), n_packages = n_distinct(ev_package), n_operations = round(mean(n_op, na.rm=TRUE), 2), percent_envir = ratio(sum(!is.na(envir)), n())) %>% 
  arrange(desc(n_call_sites))

@@

>>>>

Minimized:
```{r}
widespread_minimized <- E_cano %>%
  group_by(minimized) %>%
  summarize(n_call_sites = n_distinct(src_ref), proportion = ratio(n_call_sites, nb_call_sites), n_packages = n_distinct(ev_package), n_operations = round(mean(n_op, na.rm=TRUE), 2), percent_envir = ratio(n_distinct(cur_data()$src_ref[!is.na(cur_data()$envir)]),  n_call_sites)) %>% 
  arrange(desc(n_call_sites))

@@

# Accessing a slot

Accessing a slot is done with `$`, `[]` or `[[]]`.

```{r}
slot_access <- E_cano %>% filter(minimized == "$")

generalized_slot_access <- E_cano %>% filter(has_dollar | has_bracket)

nb_slot_sites <- slot_access %>% pull(src_ref) %>% n_distinct()

nb_generalized_slot_sites <- generalized_slot_access %>% pull(src_ref) %>% n_distinct()

r("nb slot access", nb_slot_sites)
r("slot access percent", ratio(nb_slot_sites, nb_call_sites))
r("generalized slot access", nb_generalized_slot_sites)
r("generalized slot access percent", ratio(nb_generalized_slot_sites, nb_call_sites))
```

### 2021-03-18 paper/main.tex
Analyzing expression vs analyzing evaluation of expression
Correct the percentage of non-default environments.

We classify the resolved expressions to take into account the structure of the expression passed to \eval.
However, we do not want to discriminate expressions based on specific values. Hence, the expression goes through several simplification steps: constant folding of arithmetic and string expressions that use commonly used functions (addition, string concatenation), discarding of specific value to a symbolic value holder, variable absorption. We keep track of variables, as they are evaluated in the environment specified to \eval, contrary to values that are left unchanged. We also track whether assignment operators are used in the expression or not. After the simplification steps, we obtain 15 different \emph{minimized} expressions, of which we show the ten first most frequent in numbers of sites in Table~\ref{tab:minimizedexpressions}.

\begin{table}[h]
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		Minimized & \#sites & \%sites & \#packages & \#operations & \%envir \\
		\hline
		\texttt{X} & \packageMinimizedcallsitesa  & \packageMinimizedpropsitesa & \packageMinimizedpackagea & \packageMinimizedoperationsaRnd & \packageMinimizedpercentenvira \\
		\hline
		\texttt{F(F())} & \packageMinimizedcallsitesb  & \packageMinimizedpropsitesb & \packageMinimizedpackageb  & \packageMinimizedoperationsbRnd & \packageMinimizedpercentenvirb \\
		\hline
		\texttt{V} & \packageMinimizedcallsitesc & \packageMinimizedpropsitesc & \packageMinimizedpackagec & \packageMinimizedoperationscRnd & \packageMinimizedpercentenvirc \\
		\hline
		\texttt{F(X)}& \packageMinimizedcallsitesd & \packageMinimizedpropsitesd & \packageMinimizedpackaged & \packageMinimizedoperationsdRnd & \packageMinimizedpercentenvird \\
		\hline
		\texttt{model.frame} & \packageMinimizedcallsitese & \packageMinimizedpropsitese & \packageMinimizedpackagee & \packageMinimizedoperationseRnd & \packageMinimizedpercentenvire \\
		\hline
		\texttt{\$}& \packageMinimizedcallsitesf & \packageMinimizedpropsitesf & \packageMinimizedpackagef & \packageMinimizedoperationsfRnd & \packageMinimizedpercentenvirf \\
		\hline
		\texttt{F()}& \packageMinimizedcallsitesg & \packageMinimizedpropsitesg & \packageMinimizedpackageg & \packageMinimizedoperationsgRnd & \packageMinimizedpercentenvirg \\
		\hline
		\texttt{<-} & \packageMinimizedcallsitesh & \packageMinimizedpropsitesh & \packageMinimizedpackageh & \packageMinimizedoperationshRnd & \packageMinimizedpercentenvirh \\
		\hline
		\texttt{FUN} & \packageMinimizedcallsitesi  & \packageMinimizedpropsitesi & \packageMinimizedpackagei & \packageMinimizedoperationsiRnd & \packageMinimizedpercentenviri \\
		\hline
		\texttt{\{BLOCK\}} & \packageMinimizedcallsitesj & \packageMinimizedpropsitesj & \packageMinimizedpackagej & \packageMinimizedoperationsjRnd & \packageMinimizedpercentenvirj \\
		\hline
		\texttt{F(F(<-))} & \packageMinimizedcallsitesk & \packageMinimizedpropsitesk & \packageMinimizedpackagek & \packageMinimizedoperationskRnd & \packageMinimizedpercentenvirk \\
		\hline
	\end{tabular}
	\caption{Minimized expressions: ten most frequent in terms of sites. \#sites is the number of sites; \%sites the percentage of sites across the total number of sites (\packageNbCallSites sites) with at least this minimized expression; \#packages is the number of packages with at least one of the minimized expression and measures how widespread a minimized expression is. \#operations is the average number of steps performed by the R interpreter when given that minimized expression, and \%envir is the percentage of call sites for which the \c{envir} argument is explicitly passed.} \label{tab:minimizedexpressions}
\end{table}

Note that a site can exhibit several minimized expressions. However, \packageNbOneMinimizedPercent of the sites have only one minimized expression.

@@

Similarly, when a function is evaluated on some variable (\c{F(X)}), the percentage of non default environment is high, \packageMinimizedpercentenvird\%.

@@

\section{The dangers of \eval}

>>>>

We classify the resolved expressions to take into account the structure of the expression passed to \eval.
However, we do not want to discriminate expressions based on specific values. Hence, the expression goes through several simplification steps: constant folding of arithmetic and string expressions that use commonly used functions (addition, string concatenation), discarding of specific value to a symbolic value holder, variable absorption. We keep track of variables, as they are evaluated in the environment specified to \eval, contrary to values that are left unchanged. We also track whether assignment operators are used in the expression or not. After the simplification steps, we obtain 15 different \emph{minimized} expressions, of which we show the eleven first most frequent in number of sites in Table~\ref{tab:minimizedexpressions}.

\begin{table}[h]
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		Minimized & \#sites & \%sites & \#packages & \#operations & \%envir \\
		\hline
		\texttt{X} & \packageMinimizedcallsitesa  & \packageMinimizedpropsitesa & \packageMinimizedpackagea & \packageMinimizedoperationsaRnd & \packageMinimizedpercentenvira \\
		\hline
		\texttt{F(F())} & \packageMinimizedcallsitesb  & \packageMinimizedpropsitesb & \packageMinimizedpackageb  & \packageMinimizedoperationsbRnd & \packageMinimizedpercentenvirb \\
		\hline
		\texttt{V} & \packageMinimizedcallsitesc & \packageMinimizedpropsitesc & \packageMinimizedpackagec & \packageMinimizedoperationscRnd & \packageMinimizedpercentenvirc \\
		\hline
		\texttt{F(X)}& \packageMinimizedcallsitesd & \packageMinimizedpropsitesd & \packageMinimizedpackaged & \packageMinimizedoperationsdRnd & \packageMinimizedpercentenvird \\
		\hline
		\texttt{model.frame} & \packageMinimizedcallsitese & \packageMinimizedpropsitese & \packageMinimizedpackagee & \packageMinimizedoperationseRnd & \packageMinimizedpercentenvire \\
		\hline
		\texttt{\$}& \packageMinimizedcallsitesf & \packageMinimizedpropsitesf & \packageMinimizedpackagef & \packageMinimizedoperationsfRnd & \packageMinimizedpercentenvirf \\
		\hline
		\texttt{F()}& \packageMinimizedcallsitesg & \packageMinimizedpropsitesg & \packageMinimizedpackageg & \packageMinimizedoperationsgRnd & \packageMinimizedpercentenvirg \\
		\hline
		\texttt{<-} & \packageMinimizedcallsitesh & \packageMinimizedpropsitesh & \packageMinimizedpackageh & \packageMinimizedoperationshRnd & \packageMinimizedpercentenvirh \\
		\hline
		\texttt{FUN} & \packageMinimizedcallsitesi  & \packageMinimizedpropsitesi & \packageMinimizedpackagei & \packageMinimizedoperationsiRnd & \packageMinimizedpercentenviri \\
		\hline
		\texttt{\{BLOCK\}} & \packageMinimizedcallsitesj & \packageMinimizedpropsitesj & \packageMinimizedpackagej & \packageMinimizedoperationsjRnd & \packageMinimizedpercentenvirj \\
		\hline
		\texttt{F(F(<-))} & \packageMinimizedcallsitesk & \packageMinimizedpropsitesk & \packageMinimizedpackagek & \packageMinimizedoperationskRnd & \packageMinimizedpercentenvirk \\
		\hline
	\end{tabular}
	\caption{Minimized expressions: eleven most frequent in number of sites. \#sites is the number of sites; \%sites the percentage of sites across the total number of sites (\packageNbCallSites sites) with at least this minimized expression; \#packages is the number of packages with at least one of the minimized expression and measures how widespread a minimized expression is. \#operations is the average number of steps performed by the R interpreter when given that minimized expression, and \%envir is the percentage of call sites for which the \c{envir} argument is explicitly passed.} \label{tab:minimizedexpressions}
\end{table}

Note that a site can exhibit several minimized expressions. However, \packageNbOneMinimizedPercent of the sites have only one minimized expression. Note also that if a function is called in that expression, we see only the function call but not the body of the function. We will trace what happens during the evaluation of the expression by \eval in Section~\ref{sec:dangerseval}, especially about side effects performed in \eval.

@@

Similarly, when a function is evaluated on some variable (\c{F(X)} minimized expression), the percentage of non default environment is high, \packageMinimizedpercentenvird\%.

@@

\section{The dangers of \eval} \label{sec:dangerseval}
